```yaml
---
title: "Fast Variable Selection with GIC in High Dimension via Hopfield Network"
author: "Yuchen Xiao"
date: "2025-04-10"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fast Variable Selection with GIC in High Dimension via Hopfield Network}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE  # Prevent Julia-dependent code from running on CRAN
)
```

## Overview

The `GICHighDimension` package enables variable selection in high-dimensional regression models using the generalized information criterion ('GIC') and a Hopfield-inspired optimization routine. It leverages 'Julia' for performance-critical computations and supports generalized linear models ('GLMs') such as 'Normal', 'Poisson', and 'MultivariateNormal'.

This vignette demonstrates how to:

- Generate synthetic high-dimensional data
- Run `GICSelection()` for model selection
- Interpret selection output

## Julia Setup (Optional)

To use this package, 'Julia' (≥ 1.9.0) must be available and initialized.

```{r}
# Initialize Julia (optional)
library(GICHighDimension)
setup_julia(install_julia = FALSE, quiet = TRUE)
```

## Example: Univariate Normal Selection

```{r}
n <- 100
p <- 30
k <- 3
X <- matrix(rnorm(n * p), n, p)
true_beta <- numeric(p)
true_beta[sample(1:p, k)] <- 2
Y <- LP_to_Y(X, true_beta, family = "Normal")

result <- GICSelection(
  X = X,
  Y = Y,
  Initial_Column = 1:p,
  Calculate_GIC = "Calculate_SIC",
  Calculate_GIC_short = "Calculate_SIC_short",
  Nsim = 3
)

str(result$selected_coeffs)
```

## Notes

- All Julia-based code is wrapped with `eval = FALSE` to comply with CRAN policy.
- Users must install and configure 'Julia' separately. See `setup_julia()` for more.
